Backpropagating Gravitational wave events

### 2022-03-21 src/ms.tex
Add table. Need formatting

In principle, we should only accept solutions that exactly reproduce the LVK posterior samples in the observable space.
However, it is not feasible to achieve such condition in practice, therefore we relax the condition in eq.\ref{eq:loss} to a small acceptance threshold, in our case we picked $10^{-2}$.
To make sure we find a reasonably complete set of progenitor parameters that corresponds to the posterior sample point, we use 1000 different initial guesses in solving the optimization problem.
As long as the solution fulfill the acceptance criteria, the root is as valid as all other roots that fulfill the same acceptance criteria, regardless to its initial guess.
In other word, we have the freedom to choose the set of initial guesses however we think it might benefit the optimization.
Most of the points in the evolutionary parameter space do not produce mergers, and for systems that do not merge, we set the binary masses to be 0.
This means the gradient for systems that do not merge is 0, and the root finder would likely to get stuck in such state during the first step.\footnote{On a plateau of constant loss, the root finder performs no better than a random guess. In a high dimensional space, this means the root finder will need a long time to get close to a solution.}
Therefore, it is beneficial to put initial guesses in region of the evolutionary parameter space that does produce merger.
To construct a list of initial guesses, we evolve a set of points that we uniformly sampled from the evolutionary parameter space, then keep the points that merge within a Hubble time.
%Note that this freedom in choosing the initial guess introduces a subtlety in interpreting the posterior in the evolutionary parameter space. \kw{continue explaining}

% \kw{There is a caveat to this initialization. Imagine there are two clusters of posterior points in the evolutionary parameter space, one with N points and one with M points, do we treat each cluster as one point? Or do we give equal weight to each root? This is probably a choice at the end which matters a little bit, and depends on the prior choice, but we should clear the conceptual confusion.
% Perhaps we can put a heuristic experiment result in appendix: we randomly sample the possible root for each posterior, then use that as the result, and we do it multiple times to show the result doesn't change dramatically.
% Prior weight across posterior samples may help to alleviate the issue.}
% \kw{The most robust thing one can do is sample the prior in the evolationary parameter space, pipe it through BSE then the GW PE code. I think it is still subject to the same multiple root problem, and N-M problem will still be there.
% So in a sense, the only prior we have to take care is really the GW prior.}
% \kw{Mention how we generate the initial guesses.}

@@

We show a portion of the joint posterior of the progenitor parameters and hyper-parameters of GW150914 in figure \ref{fig:GW150914_posterior}.
\kw{Recover ratio of the posterior sample goes here.}

@@

\begin{figure*}
\includegraphics[width=0.98\textwidth]{static/GW150914_corner.pdf}
\caption{The posterior for GW150914 in both the progenitor parameter space and hyper-parameter space.
$M_1$ and $M_2$ are the progenitors' masses. $\log{t_{orb}}, e, \log{Z}$ are the progenitor binary's log orbital period, eccentricity and log metallicity at ZAMS.
$\alpha$ is the common envelope efficiency.
$f_{\rm acc}$ is the fraction of mass accreted during stable mass transfer.
$q_{\rm crit 3,4}$ are the critical mass during \kw{Katie fill in},
$\sigma$ is the mean magnitude of the Maxwellian distribution characterizing natal kick strength.
}
\label{fig:GW150914_posterior}
\end{figure*}

>>>>

In principle, we should only accept solutions that exactly reproduce the LVK posterior samples in the observable space.
However, it is not feasible to achieve such condition in practice, therefore we relax the condition in eq.\ref{eq:loss} to a small acceptance threshold, in our case we picked $10^{-2}$ to be our threshold.
To make sure we find a reasonably complete set of progenitor parameters that corresponds to the posterior sample point, we use 1000 different initial guesses in solving the optimization problem.
As long as the solution fulfill the acceptance criteria, the root is as valid as all other roots that fulfill the same acceptance criteria, regardless to its initial guess.
In other word, we have the freedom to choose the set of initial guesses however we think it might benefit the optimization.
Most of the points in the evolutionary parameter space do not produce mergers, and for systems that do not merge, we set the binary masses to be 0.
This means the gradient for systems that do not merge is 0, and the root finder would likely to get stuck in such state during the first step.\footnote{On a plateau of constant loss, the root finder performs no better than a random guess. In a high dimensional space, this means the root finder will need a long time to get close to a solution.}
Therefore, it is beneficial to put initial guesses in region of the evolutionary parameter space that does produce merger.
To construct a list of initial guesses, we evolve a set of points that we uniformly sampled from the evolutionary parameter space, then keep the points that merge within a Hubble time.

@@

\begin{table*}[h!]
    \begin{center}
    \begin{tabular}{ l l l }
    \hline
    \hline
    Parameters &  Description & Optimization range\\
    \hline
    \hline
    Observables &\ &\  \\
    \hline
    \hline
    $M_{\rm GW,1}$ & primary mass of the GW event & NA \\
    $M_{\rm GW,2}$ & secondary mass of the GW event  & NA\\
    \hline
    \hline
    Progenitor parameters &\ &\  \\
    \hline
    \hline
    $M_{\rm ZAMS,1}$ & primary mass at ZAMS & $[10,150]\ M_{\odot}$\\
    $M_{\rm ZAMS,2}$ & secondary mass at ZAMS & $[10,150]\ M_{\odot}$\\
    $t_{\rm orb}$ & orbital period at ZAMS & $[5,5000]$ days\\
    $e$ & eccentricity at ZAMS & $[0,1]$\\
    $Z$ & metallicity at ZAMS & $[10^{-4},2\times10^{-2}]$\\
    $z$ & redshift at ZAMS & NA\\
    \hline
    \hline
    Hyper-parameters &\ &\ \\
    \hline
    \hline

    $\alpha$ & common envelope efficiency & $[0.1,10]$\\
    $f_{\rm acc}$ & fraction of accretion during stable mass transfer & $[0,1]$\\
    $q_{\rm crit,3}$ & & $[0.1,10]$\\
    $\sigma$ & mean natal kick magnitude & $[10,300]\ {\rm km/h}$\\

    \hline
    \hline
    \end{tabular}
    \caption{A list of parameters we used in this study.}
    \label{tab:parameters}
    \end{center}
\end{table*}

We apply the method described in section \ref{sec:method} to the first GW events GW150914.
The parameters involved in the analysis are tabulated in table \ref{tab:parameters}.

and we show a portion of the joint posterior of the progenitor parameters and hyper-parameters of GW150914 in figure \ref{fig:GW150914_posterior}.

\kw{Recover ratio of the posterior sample goes here.}

@@

\begin{figure*}[h!]
\includegraphics[width=0.98\textwidth]{static/GW150914_corner_zoomed.pdf}
\caption{The posterior for GW150914 in both the progenitor parameter space and hyper-parameter space.
$M_1$ and $M_2$ are the progenitors' masses. $\log{Z}$ is log metallicity at ZAMS.
$z$ is the redshift at ZAMS. 
$\alpha$ is the common envelope efficiency.
$f_{\rm acc}$ is the fraction of mass accreted during stable mass transfer.
$q_{\rm crit 3}$ are the critical mass during \kw{Katie fill in},
Note that the redshift is not fitted during the root finding process.
Once we have find the evolutionary parameters, we add the time it would take the progenitor to merge to the lookback time of the observed posterior sample,
then from the total lookback time we can compute the redshift at ZAMS.
}
\label{fig:GW150914_posterior}
\end{figure*}
